Associations_PFN_Cognition

### 2023-04-20 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
Update Associations_PFN_Cognition.Rmd

# harmonize TRAIN set 
batch <- abcd.data.train$abcd_site
abcd.data.train.toharmonize <- abcd.data.train[,c("PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17","thompson_PC1","thompson_PC2","thompson_PC3","meanFD")]
mod <- model.matrix(~abcd.data.train$interview_age+abcd.data.train$sex+abcd.data.train$rel_family_id)
dat <- t(abcd.data.train.toharmonize)
abcd.data.combat <- neuroCombat(dat=dat,mod=mod,batch=batch,eb=FALSE)
dat.harmonized<-data.frame(t(abcd.data.combat$dat.combat))
abcd.data.noPFNsCog <- subset(abcd.data.train,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,thompson_PC1,thompson_PC2,thompson_PC3,meanFD))
abcd.data.train.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe (BE AWARE THAT NOT ALL DATA IS HARMONIZED)

>>>>

# harmonize TRAIN set 
batch <- abcd.data.train$abcd_site
abcd.data.train.toharmonize <- abcd.data.train[,c("PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17","thompson_PC1","thompson_PC2","thompson_PC3","meanFD")]
mod <- model.matrix(~abcd.data.train$interview_age+abcd.data.train$sex+abcd.data.train$rel_family_id)
dat <- t(abcd.data.train.toharmonize)
abcd.data.combat <- neuroCombat(dat=dat,mod=mod,batch=batch,eb=FALSE)
dat.harmonized<-data.frame(t(abcd.data.combat$dat.combat))
abcd.data.noPFNsCog <- subset(abcd.data.train,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,thompson_PC1,thompson_PC2,thompson_PC3,meanFD))
abcd.data.train.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe
